Forecasting the old-age dependency ratio to determine the best pension age

### 2020-05-03 PensionAge.Rmd
New Australian data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, messages = FALSE, warning = FALSE, cache = TRUE)
# Make sure you have the latest version of rmarkdown and bookdown
# devtools::install_github("rstudio/rmarkdown")
# devtools::install_github("rstudio/bookdown")
# And the latest versions of Our packages
# devtools::install_github("robjhyndman/forecast")
# devtools::install_github("robjhyndman/demography")
# devtools::install_github("robjhyndman/addb")
library(demography)
library(addb)
library(ggplot2)
library(kableExtra)
source("functions-v4.R")
```

@@

```{r changespension, echo=FALSE, fig.cap="Government's adjustments on pension age scheme.", fig.height=4, fig.width=8, message=FALSE, warning=FALSE}
year <- 2057 - 2007
proposed <- ts(pmin(
  70,
  c(rep(65, 2017 - 2008), 65 + cumsum(rep(c(0.5, 0), 55)))
)[1:50],
start = 2008
)
approved <- pmin(proposed, 67)
current <- pmin(proposed, 65)
cols <- c(current = "#1b9e77", approved = "#d95f02", proposed = "#7570b3")
ggplot() +
  forecast::autolayer(proposed, series = "proposed") +
  forecast::autolayer(approved, series = "approved") +
  forecast::autolayer(current, series = "current") +
  xlab("Year") + ylab("Age of retirement") +
  scale_color_manual(
    values = cols, name = " ",
    breaks = c("current", "approved", "proposed"),
    labels = c("Pension age at 65", "Approved change", "Proposed further change")
  )
```

@@

```{r getdata, include=FALSE}
############################
## GET ALL THE DATA
############################

# HMD credentials
username <- "shl8858@telstra.com"
password <- "hshang85"

hmd.pop <- function (country, username, password, label = country) 
{
    path <- paste("https://www.mortality.org/hmd/", country, "/STATS/", 
        "Population.txt", sep = "")
    userpwd <- paste(username, ":", password, sep = "")
    txt <- RCurl::getURL(path, userpwd = userpwd)
    con <- textConnection(txt)
    pop <- try(utils::read.table(con, skip = 2, header = TRUE, 
        na.strings = "."), TRUE)
    close(con)
    if (class(pop) == "try-error") 
        stop("Population file not found at www.mortality.org")
    obj <- list(type = "population", label = label, lambda = 0)
    obj$year = sort(unique(pop[, 1]))
    n <- length(obj$year)
    m <- length(unique(pop[, 2]))
    obj$age <- pop[1:m, 2]
    mnames <- names(pop)[-c(1, 2)]
    n.pop <- length(mnames)
    obj$pop <- list()
    for (i in 1:n.pop) {
        obj$pop[[i]] <- matrix(pop[, i + 2], nrow = m, ncol = n)
        obj$pop[[i]][obj$pop[[i]] < 0] <- NA
        dimnames(obj$pop[[i]]) <- list(obj$age, obj$year)
    }
    names(obj$pop) <- tolower(mnames)
    obj$age <- as.numeric(as.character(obj$age))
    if (is.na(obj$age[m])) 
        obj$age[m] <- 2 * obj$age[m - 1] - obj$age[m - 2]
    return(structure(obj, class = "demogdata"))
}

hmd.mx <- function (country, username, password, label = country) 
{
    path <- paste("https://www.mortality.org/hmd/", country, "/STATS/", 
        "Mx_1x1.txt", sep = "")
    userpwd <- paste(username, ":", password, sep = "")
    txt <- RCurl::getURL(path, userpwd = userpwd)
    con <- textConnection(txt)
    mx <- try(utils::read.table(con, skip = 2, header = TRUE, 
        na.strings = "."), TRUE)
    close(con)
    if (class(mx) == "try-error") 
        stop("Connection error at www.mortality.org. Please check username, password and country label.")
    path <- paste("https://www.mortality.org/hmd/", country, "/STATS/", 
        "Exposures_1x1.txt", sep = "")
    userpwd <- paste(username, ":", password, sep = "")
    txt <- RCurl::getURL(path, userpwd = userpwd)
    con <- textConnection(txt)
    pop <- try(utils::read.table(con, skip = 2, header = TRUE, 
        na.strings = "."), TRUE)
    close(con)
    if (class(pop) == "try-error") 
        stop("Exposures file not found at www.mortality.org")
    obj <- list(type = "mortality", label = label, lambda = 0)
    obj$year <- sort(unique(mx[, 1]))
    n <- length(obj$year)
    m <- length(unique(mx[, 2]))
    obj$age <- mx[1:m, 2]
    mnames <- names(mx)[-c(1, 2)]
    n.mort <- length(mnames)
    obj$rate <- obj$pop <- list()
    for (i in 1:n.mort) {
        obj$rate[[i]] <- matrix(mx[, i + 2], nrow = m, ncol = n)
        obj$rate[[i]][obj$rate[[i]] < 0] <- NA
        obj$pop[[i]] <- matrix(pop[, i + 2], nrow = m, ncol = n)
        obj$pop[[i]][obj$pop[[i]] < 0] <- NA
        dimnames(obj$rate[[i]]) <- dimnames(obj$pop[[i]]) <- list(obj$age, 
            obj$year)
    }
    names(obj$pop) = names(obj$rate) <- tolower(mnames)
    obj$age <- as.numeric(as.character(obj$age))
    if (is.na(obj$age[m])) 
        obj$age[m] <- 2 * obj$age[m - 1] - obj$age[m - 2]
    return(structure(obj, class = "demogdata"))
}

# Get population data for 1 Jan 2015
auspop <- hmd.pop(country = "AUS", username = username, password = password, label = "Australia")
auspop <- extract.ages(auspop, age = 0:100)

# Get mortality data
aus.mort <- hmd.mx("AUS", username, password, "Australia")
aus.mort <- extract.years(extract.ages(aus.mort, 0:100,
  combine.upper = FALSE
),
year = 1950:max(aus.mort$year)
)

# Get fertility data:
# Need to install addb package from http://robjhyndman.com/software/addb/
library(addb) # Contains fertility data for 1921-2006
aus.fert <- aus.fertility
births <- aus.fert$rate$female * aus.fert$pop$female
# Update fertility data to 2015
ausf <- read.csv("FERTILITY_AGE_STATE_16062017173020984.csv",
  header = TRUE,
  stringsAsFactors = FALSE
)
# National births only
ausf <- ausf[ausf$Region == "Australia", ]
# Remove age aggregations
ausf <- ausf[ausf$Age %in% paste(15:49), ]
ausf[, "Age"] <- as.numeric(ausf[, "Age"])
# Extract births and population values
newbirths <- matrix(ausf[ausf$Measure == "Births", "Value"],
  nrow = nrow(births), byrow = TRUE
) * 1000
newpop <- matrix(ausf[ausf$Measure == "Female population", "Value"],
  nrow = nrow(births), byrow = TRUE
) * 1000
rownames(newbirths) <- rownames(newpop) <- 15:49
colnames(newbirths) <- colnames(newpop) <- 2004:2015
births <- cbind(births[, 1:83], newbirths)
fpop <- cbind(aus.fert$pop$female[, 1:83], newpop / 1000)
# Use populations in ausf rather than auspop to get the same rates
aus.fert$rate$female <- births / fpop
aus.fert$pop$female <- fpop
aus.fert$year <- 1921:2015

aus.fert_v0 = extract.years(aus.fert, 1921:2014)

##### MIGRATION
aus.mig <- netmigration(mort = aus.mort, fert = aus.fert_v0, mfratio = 1.05)
```

```{r smoothing, dependson='getdata'}
################################################
################ SMOOTHING STEP ################
################################################

ausmort.sm <- smooth.demogdata(aus.mort, obs.var = "theoretical")
ausfert.sm <- smooth.demogdata(aus.fert_v0, obs.var = "theoretical")
ausmig.sm <- smooth.demogdata(aus.mig)
```

@@

```{r componentsfertility, fig.cap="Fitted basis functions and coefficients for Australian age-specific fertility rates.", dependson='models'}
par(mgp = c(2.2, 0.45, 0), tcl = -0.4, mar = c(3.3, 3.6, 1.1, 1.1))
plot(fertf, "c", comp = 2)
```

@@

```{r simulation, dependson='models'}
############### SIMULATION STEP #################
# This takes a while!
set.seed(2019-01-13)
nsim <- 20 # Change to 2000 or higher to get better estimates
aus.sim <- pop.sim(mort = mortf, fert = fertf, mig = migf, firstyearpop = auspop, N = nsim)
```

```{r simulationresults}
## Means and intervals
popm.mean <- apply(aus.sim$male, c(1, 2), mean, na.rm = TRUE)
popm.lo <- apply(aus.sim$male, c(1, 2), quantile, p = .1, na.rm = TRUE)
popm.hi <- apply(aus.sim$male, c(1, 2), quantile, p = .9, na.rm = TRUE)
popf.mean <- apply(aus.sim$female, c(1, 2), mean, na.rm = TRUE)
popf.lo <- apply(aus.sim$female, c(1, 2), quantile, p = .1, na.rm = TRUE)
popf.hi <- apply(aus.sim$female, c(1, 2), quantile, p = .9, na.rm = TRUE)

## TOTAL POPULATION COMPARISONS
totfpop <- apply(aus.sim$female, c(2, 3), sum, na.rm = TRUE)
totmpop <- apply(aus.sim$male, c(2, 3), sum, na.rm = TRUE)
totfpop.q <- apply(totfpop, 1, quantile, p = c(0.025, .1, .5, .9, .975), na.rm = TRUE) / 1e6
totmpop.q <- apply(totmpop, 1, quantile, p = c(0.025, .1, .5, .9, .975), na.rm = TRUE) / 1e6
```

```{r totalpopulationbyyears, fig.cap="Fifty-year forecasts of total population for each sex, along with 80% prediction intervals. The actually population from 1950 to 2015 is shown using circles.", fig.height=4, dependson='simulationresults'}
par(mgp = c(2.2, 0.45, 0), tcl = -0.4, mar = c(3.3, 3.6, 1.1, 1.1))
par(mfrow = c(1, 2))
fy <- fertf$year
plot(auspop$year, colSums(auspop$pop$female) / 1e6,
  xlim = c(1950, 2064),
  ylim = range(c(0, 30), na.rm = TRUE),
  xlab = "Year",
  ylab = "Population (millions)",
  main = "Total female population"
)
polygon(c(fy, rev(fy)),
  c(totfpop.q[2, ], rev(totfpop.q[4, ])),
  col = "yellow", border = FALSE
)
lines(fy, totfpop.q[3, ], lwd = 2, col = "blue")

plot(auspop$year, colSums(auspop$pop$male) / 1e6,
  xlim = c(1950, 2064),
  ylim = range(c(0, 30), na.rm = TRUE),
  xlab = "Year",
  ylab = "Population (millions)",
  main = "Total male population"
)
polygon(c(fy, rev(fy)),
  c(totmpop.q[2, ], rev(totmpop.q[4, ])),
  col = "yellow", border = FALSE
)
lines(fy, totmpop.q[3, ], lwd = 2, col = "blue")
```

```{r totalpopulationin2034, fig.cap="Forecast population pyramid for 2034, along with 80% pointwise prediction intervals. The actual pyramid for 2015 is shown using dashed lines.", , dependson='simulationresults'}
par(mgp = c(2.2, 0.45, 0), tcl = -0.4, mar = c(4.3, 3.6, 3.0, 3.3))
plot(c(0, 100), c(0, 100),
  type = "n", main = "Forecast population: 2034", yaxt = "n",
  xlab = "Population ('000)", ylab = "Age", xaxt = "n", xlim = c(-1, 1) * max(abs(popm.hi[, 20]), abs(popf.hi[, 20])) / 1e3
)
mtext("Male                       Female")
abline(v = 0)
axis(1, at = seq(-300, 0, by = 50), labels = rev(seq(0, 300, by = 50)))
axis(1, at = seq(50, 300, by = 50))
axis(2, at = seq(0, 100, by = 10), labels = seq(0, 100, by = 10))
axis(4, at = seq(0, 100, by = 10), labels = seq(0, 100, by = 10))
axis(2, at = seq(0, 100, by = 20), labels = seq(0, 100, by = 20))
axis(4, at = seq(0, 100, by = 20), labels = seq(0, 100, by = 20))
axis(4, at = 50, line = 1.5, labels = "Age", col = 2, tick = FALSE)
polygon(c(-popm.lo[, 20], rev(-popm.hi[, 20])) / 1000, c(0:100, 100:0), col = "yellow", border = FALSE)
polygon(c(popf.lo[, 20], rev(popf.hi[, 20])) / 1000, c(0:100, 100:0), col = "yellow", border = FALSE)
lines(-auspop$pop$male[, ncol(auspop$pop$male)] / 1000, 0:100, col = 1, lty = 2)
lines(auspop$pop$female[, ncol(auspop$pop$female)] / 1000, 0:100, col = 1, lty = 2)
text(100, 60,  "2015")
text(-100, 60, "2015")
lines(-popm.mean[, 20] / 1000, 0:100, col = "blue", lwd = 2)
lines(popf.mean[, 20] / 1000, 0:100, col = "blue", lwd = 2)
```

@@

```{r OADRat65, fig.cap="Fifty-year forecasts of the OADR with assumption of pension age equal to 65 for both sexes, along with 80% pointwise prediction interval.", dependson='simulationresults'}
OADR.f <- oadr(auspop, aus.sim, pension.age = current)
autoplot(OADR.f) + xlab("year") + ylab("ratio") +
  ggtitle("OADR forecasts with pension age=65")
```

```{r OADRcurrent, fig.cap="Fifty-year forecasts of the OADR associated with a pension age equal to 65 (green line) and equal to the pension age scheme with approved change (orange line) respectively, along with the desired OADR level in purple. The actual OADRs for 1950-2014 are shown in black.", dependson='OADRat65'}
OADR.f.67 <- oadr(auspop, aus.sim, pension.age = approved)
OADR.f.prop <- oadr(auspop, aus.sim, pension.age = proposed)
autoplot(OADR.f$x) +
  geom_hline(yintercept = 0.21, col = "gray") +
  autolayer(OADR.f, series = "current", alpha = 0.5) +
  autolayer(OADR.f.67, series = "approved", alpha = 0.5) +
  autolayer(OADR.f.prop, series = "proposed", alpha = 0.5) +
  ylab("ratio") + xlab("Year") +
  ggtitle("OADR forecasts") +
  scale_color_manual(
    values = cols, name = " ",
    breaks = c("current", "approved", "proposed"),
    labels = c("Pension age at 65", "Approved change", "Proposed further change")
  )
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, messages = FALSE, warning = FALSE, cache = TRUE)
library(tidyverse)
library(demography)
#remotes::install_github("robjhyndman/addb")
library(addb)
library(kableExtra)
library(patchwork)
source("functions-v4.R")
source("hmd.R")
```

@@

```{r changespension, echo=FALSE, fig.cap="Government's adjustments on pension age scheme.", fig.height=4, fig.width=8, message=FALSE, warning=FALSE}
# Policies obtained from https://www.dss.gov.au/seniors/benefits-payments/age-pension
pension_age <- tibble(
    year = 2008:2068,
    current = 65
  ) %>%
  mutate(
    proposed = pmin(70, current + 0.5*pmax(0, trunc((year - 2015)/2))),
    approved = pmin(proposed, 67),
  ) %>%
  pivot_longer(-year, values_to="age", names_to="policy")

pension_age %>%
  filter(year <= 2050) %>%
  ggplot(aes(x=year, y=age, group=policy)) +
    geom_line(aes(col=policy)) +
    xlab("Year") + ylab("Age of retirement") +
    scale_color_manual(
      values = c(current = "#1b9e77", approved = "#d95f02", proposed = "#7570b3"),
      name = " ",
      breaks = c("current", "approved", "proposed"),
      labels = c("Pension age at 65", "Approved change", "Proposed further change")
    )
```

@@

```{r getdata, eval=FALSE}
################################################
################### DATA STEP ##################
################################################

# Get population data to 1 Jan 2019
auspop <- hmd.pop(country = "AUS", username = username, password = password, label = "Australia")
auspop <- extract.ages(auspop, ages = 0:100)

# Get mortality data to 2018
aus.mort <- hmd.mx("AUS", username, password, "Australia")
aus.mort <- aus.mort %>%
  extract.ages(ages = 0:100, combine.upper = FALSE) %>%
  extract.years(years = 1950:max(aus.mort$year))

# Get fertility data for 1921-2006
aus.fert <- aus.fertility
births <- aus.fert$rate$female * aus.fert$pop$female
# Get latest fertility data from ABS (downloaded 30 April 2020)
ausf <- readr::read_csv("FERTILITY_AGE_STATE_30042020143630412.csv") %>%
  filter(
    Region == "Australia",
    Age %in% paste(15:49),
  ) %>%
  mutate(
    Year = Time,
    Age = as.numeric(Age)
  ) %>%
  select(Year, Age, Measure, Value) 
# Extract births and population values
newbirths <- ausf %>%
  filter(Measure == "Births") %>%
  mutate(Value = Value * 1000) %>%
  select(-Measure) %>%
  pivot_wider(names_from=Year, values_from=Value) %>%
  select(-Age) %>%
  as.matrix()
newpop <- ausf %>%
  filter(Measure == "Female population") %>%
  mutate(Value = Value) %>%
  select(-Measure) %>%
  pivot_wider(names_from=Year, values_from=Value) %>%
  select(-Age) %>%
  as.matrix()
rownames(newbirths) <- rownames(newpop) <- 15:49

# Use ABS data where available
births <- cbind(births[, 1:54], newbirths)
fpop <- cbind(aus.fert$pop$female[, 1:54], newpop)
# Use populations in ausf rather than auspop to get the same rates
aus.fert$rate$female <- births / fpop
aus.fert$pop$female <- fpop
aus.fert$year <- 1920 + seq(NCOL(births))

# Compute migration data
aus.mig <- netmigration(mort = aus.mort, fert = aus.fert, startyearpop = auspop, mfratio = 1.05)
save(aus.fert, aus.mort, aus.mig, file="ausdata.Rdata")
```

```{r maketibble}
load("ausdata.Rdata")

auspop_df <- bind_rows(
  as_tibble(auspop$pop$male / 1000) %>%
    mutate(
      Age = auspop$age,
      Sex = "Male"
    ) %>%
    pivot_longer(c(-Age, -Sex), names_to = "Year", values_to = "Population"),
  as_tibble(auspop$pop$female / 1000) %>%
    mutate(
      Age = auspop$age,
      Sex = "Female"
    ) %>%
    pivot_longer(c(-Age, -Sex), names_to = "Year", values_to = "Population"),
)
```

```{r smoothing}
################################################
################ SMOOTHING STEP ################
################################################

ausmort.sm <- smooth.demogdata(aus.mort, obs.var = "theoretical")
ausfert.sm <- smooth.demogdata(aus.fert, obs.var = "theoretical")
ausmig.sm <- smooth.demogdata(aus.mig)
```

@@

```{r componentsfertility, fig.cap="Fitted basis functions and coefficients for Australian age-specific fertility rates.", dependson='models'}
autoplot(fertf)
```

@@

```{r simulation, dependson='models'}
############### SIMULATION STEP #################
# This takes a while!
set.seed(2020-05-02)
nsim <- 20 # Change to 2000 or higher to get better estimates
aus.sim <- pop.sim(mort = mortf, fert = fertf, mig = migf, firstyearpop = auspop, N = nsim)
```

```{r simtibble, dependson = 'simulation}
# Combine simulation results into one tibble
dimnames(aus.sim[["male"]]) <- dimnames(aus.sim[["female"]]) <- list(
  Age = dimnames(aus.sim[[1]])[[1]],
  Year = dimnames(aus.sim[[1]])[[2]],
  Rep = dimnames(aus.sim[[1]])[[3]]
)
aussim_df <- bind_rows(
  as.tbl_cube(aus.sim[["male"]]/1e3, met_name = "Population") %>% 
    as_tibble() %>% mutate(Sex = "Male"),
  as.tbl_cube(aus.sim[["female"]]/1e3, met_name = "Population") %>% 
    as_tibble() %>% mutate(Sex = "Female")
)
#rm(aus.sim)
# Combine simulations to create means and quantiles of future years
future_pop <- aussim_df %>%
  group_by(Sex, Age, Year) %>%
  summarise(
    Mean = mean(Population),
    Lower = quantile(Population, prob=0.1),
    Upper = quantile(Population, prob=0.9)
  ) %>%
  ungroup()
future_tot_pop <- aussim_df %>%
  group_by(Rep, Sex, Year) %>%
  summarise(Population = sum(Population)/1e3) %>%
  group_by(Sex, Year) %>%
  summarise(
    Mean = mean(Population),
    Median = median(Population),
    Lo95 = quantile(Population, prob=0.025),
    Up95 = quantile(Population, prob=0.975),
    Lo80 = quantile(Population, prob=0.1),
    Up80 = quantile(Population, prob=0.9)
  ) %>%
  ungroup()
# Historical data as a tibble
history_pop <- bind_rows(
  as_tibble(auspop$pop$male / 1000) %>%
    mutate(
      Age = auspop$age,
      Sex = "Male"
    ) %>%
    pivot_longer(c(-Age, -Sex), names_to = "Year", values_to = "Population"),
  as_tibble(auspop$pop$female / 1000) %>%
    mutate(
      Age = auspop$age,
      Sex = "Female"
    ) %>%
    pivot_longer(c(-Age, -Sex), names_to = "Year", values_to = "Population"),
  ) %>%
  mutate(Year = as.numeric(Year))
history_tot_pop <- history_pop %>%
  group_by(Sex, Year) %>%
  summarise(Population = sum(Population)/1e3)
```

```{r totalpopulationbyyears, fig.cap="Fifty-year forecasts of total population for each sex, along with 80% prediction intervals. The actually population from 1950 to 2015 is shown using circles.", fig.height=4, dependson='simulationresults'}
history_tot_pop %>% 
  ggplot(aes(x=Year, y=Population, group=Sex)) +
    geom_line(size=1) +
    ylab("Population (millions)") + 
    ggtitle("Total population") +
    facet_grid(. ~ Sex) +
    geom_ribbon(aes(y=Mean, ymin=Lo80, ymax=Up80), fill='#7d7def', data=future_tot_pop) +
    geom_line(data=future_tot_pop, col='blue', mapping=aes(y=Mean), size=1) 
```

```{r totalpopulationin2034, fig.cap="Forecast population pyramid for 2034, along with 80% pointwise prediction intervals. The actual pyramid for 2015 is shown using dashed lines.", , dependson='simulationresults'}
pyramid <- function(history, future) {
  data <- bind_rows(history, future)
  p_male <- data %>%
    filter(Sex == "Male") %>%
    ggplot(aes(x = Age, y = Population, group=Year)) +
      labs(y = "Population ('000)") +
      geom_ribbon(aes(x=Age, ymin=Lower, ymax=Upper, y=Mean), fill='#7d7def') +
      geom_line(linetype=2) + geom_line(aes(y=Mean), col='blue') + 
      coord_flip() +
      scale_y_reverse(expand=c(0.012, 0.012)) +
      scale_x_continuous(expand=c(0.012,0.012)) +
      facet_grid(. ~ Sex)
  p_female <- data %>%
    filter(Sex == "Female") %>%
    ggplot(aes(x = Age, y = Population, group=Year)) +
      labs(y = "Population ('000)") +
      geom_ribbon(aes(x=Age, ymin=Lower, ymax=Upper, y=Mean), fill='#7d7def') +
      geom_line(linetype=2) + geom_line(aes(y=Mean), col='blue') + 
      coord_flip() +
      scale_y_continuous(expand=c(0.012,0.012)) +
      theme(axis.title.y.left=element_blank(),
        axis.text.y.left=element_blank(),
        axis.ticks.y.left=element_blank()) +
      scale_x_continuous(position="top", sec.axis = sec_axis(~ .), expand=c(0.012,0.012)) +
      facet_grid(. ~ Sex)

  (p_male | p_female) 
}
pyramid(
  history_pop %>% filter(Year == max(Year)),
  future_pop %>% filter(Year == max(history_pop$Year) + 20) 
)
```

@@

```{r OADRat65, fig.cap="Fifty-year forecasts of the OADR with assumption of pension age equal to 65 for both sexes, along with 80% pointwise prediction interval.", dependson='simulationresults'}
current <- pension_age %>% 
  filter(policy=="current", year %in% unique(tot_pop$Year) ) %>% 
  arrange(year) %>% pull(age)
proposed <- pension_age %>% 
  filter(policy=="proposed", year %in% unique(tot_pop$Year) ) %>% 
  arrange(year) %>% pull(age)
approved <- pension_age %>% 
  filter(policy=="approved", year %in% unique(tot_pop$Year) ) %>% 
  arrange(year) %>% pull(age)
OADR.65 <- oadr(history, aussim_df, pension.age = current) %>% mutate(policy="Pension age 65")
OADR.65 %>%
  ggplot(aes(x=Year, y=OADP, group=Sex)) +
    geom_ribbon(aes(ymin=Lo, ymax=Hi), fill='#7d7def') +
    geom_line(col='blue', size=1) +
    facet_grid(. ~ Sex) +
    xlab("year") + ylab("ratio") +
    ggtitle("OADR forecasts with pension age=65")
```

```{r OADRcurrent, fig.cap="Fifty-year forecasts of the OADR associated with a pension age equal to 65 (green line) and equal to the pension age scheme with approved change (orange line) respectively, along with the desired OADR level in purple. The actual OADRs for 1950-2014 are shown in black.", dependson='OADRat65'}
OADR.67 <- oadr(history, aussim_df, pension.age = approved) %>% 
  mutate(policy="Current policy")
OADR.prop <- oadr(history, aussim_df, pension.age = proposed) %>% 
  mutate(policy="Proposed policy")
bind_rows(OADR.65,OADR.67,OADR.prop) %>%
  mutate(policy = factor(policy, 
    levels = c("Pension age 65","Current policy","Proposed policy"))) %>%
  ggplot(aes(x=Year, y=OADP, group=policy)) +
    geom_ribbon(aes(ymin=Lo, ymax=Hi, fill=policy), alpha=0.5) +
    geom_line(aes(col=policy), size=1) +
    geom_hline(yintercept = 0.21, col = "gray") +
    facet_grid(. ~ Sex) +
    xlab("year") + ylab("ratio") +
    ggtitle("OADR forecasts with pension age=65") +
    scale_color_brewer(palette="Dark2") + scale_fill_brewer(palette="Dark2")
```
